### 2008-09-22 doc/a-rex/arex_tech_doc.tex
Adding referencce to backends documentation - better than nothing
Implementing A-REX doc changes from Steffen.

%% LyX 1.4.5.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[twoside,english]{article}
\usepackage{pslatex}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{geometry}
\geometry{verbose,a4paper,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\usepackage{array}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{setspace}
\onehalfspacing
\usepackage{amssymb}
\IfFileExists{url.sty}{\usepackage{url}}
                      {\newcommand{\url}{\texttt}}

@@

A-REX is one of ARC middleware components that implements functions
of so called \emph{Computing Element} (CE).

@@

>>>>

%% LyX 1.4.5 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[twoside,english]{article}
\usepackage{pslatex}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{geometry}
\geometry{verbose,a4paper,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\usepackage{array}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{setspace}
\onehalfspacing
\usepackage{amssymb}
\IfFileExists{url.sty}{\usepackage{url}}
                      {\newcommand{\url}{\texttt}}

@@

A-REX is one of ARC middleware components that implements functions
of the so called \emph{Computing Element} (CE). Here Computing Element
is a service accepting requests containing description of generic
computational job and executing it in underlying local batch system.

@@

For information about supported LRMSes and their specific features
and configuration options please read dedicated documentation at \cite{backends-arc1}.
